ODGI: understanding pangenome graphs

### 2021-11-04 manuscript/main.tex
data

\FIXME{Data used to build Human pangenome graphs is available at \url{https://github.com/human-pangenomics/HPP_Year1_Data_Freeze_v1.0}.}
Code used to build images in this manuscript is available at \url{https://github.com/pangenome/odgi-paper}.
TODO!

>>>>

Data used to build human pangenome graphs: \url{https://github.com/human-pangenomics/HPP_Year1_Data_Freeze_v1.0}.
Code used to build this manuscript and its figures: \url{https://github.com/pangenome/odgi-paper}.
